On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/experiments.tex
Experiments - table with columns for finetuning. Missing dot in the intro
double --
tiny changes
Added precise training time.

\begin{table}[]
	\caption{CLEVR \& CoGenT accuracies for the MAC \& simplified MAC models}
	\centering
	\begin{tabular}{cccccc}
		\toprule
		Model                 & Training set                & Training time [h] & Training acc [\%]          & Test set & Test acc [\%] \\
		\midrule
		\multirow{3}{*}{MAC}  & CLEVR                       & 31                                   & acc: 96.7                  & CLEVR    & 96.2          \\
		\cmidrule{2-6} 
		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31}                    & \multirow{2}{*}{acc: 97.0} & CoGenT-A & 96.9         \\
		\cmidrule{5-6} 
		&                             &                                         &                              & CoGenT-B & 79.5          \\
		\midrule
		\multirow{3}{*}{SMAC} & CLEVR                       & 28                                     & acc: 95.8               & CLEVR    & 95.3          \\
		\cmidrule{2-6} 
		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28}                    & \multirow{2}{*}{acc: 96.1} & CoGenT-A & 95.9          \\
		\cmidrule{5-6} 
		&                             &                                         &                              & CogenT-B & 78.7          \\
		\bottomrule
	\end{tabular}
	\label{results}
\end{table}

We report the obtained scores in \tableref{results}. Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31h of training.\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
Evaluating MAC on CoGenT shows that, like previous work (\cite{johnson2017inferring}, \cite{mascharka2018transparency})], the performance is worse on Condition B than Condition A after training only using Condition A data. As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, which surpasses the previously 78.8\% reported in \cite{perez2017film}. \tk{not sure why we report this, is it state-of-the-art?}
The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score. Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of ~10\% in wall time. This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.

>>>>

\begin{table}[]
	\caption{CLEVR \& CoGenT accuracies for the MAC \& simplified MAC models}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		\multirow{3}{*}{MAC}  & CLEVR                       & 31.86         &  --   & --                     & 96.7                  & CLEVR    & 96.2          \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31.86}     &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{97.0} & CoGenT-A & 96.9         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B & 79.5          \\
		\midrule
		\multirow{3}{*}{SMAC} & CLEVR                       & 28.51      &   --   &   --                 & 95.8               & CLEVR    & 95.3          \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28.55}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{96.1} & CoGenT-A & 95.9          \\
		\cmidrule{7-8} 
		&                             &                                         &     &          &                & CogenT-B & 78.7          \\
		\bottomrule
	\end{tabular}
	\label{results}
\end{table}

We report the obtained scores in \tableref{results}. Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31h of training.\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
Evaluating MAC on CoGenT shows that, like previous work (\cite{johnson2017inferring}, \cite{mascharka2018transparency})], the performance is worse on Condition B than Condition A after training only using Condition A data. As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, which surpasses the previously 78.8\% reported in \cite{perez2017film}. \tk{not sure why we report this, is it state-of-the-art?}
The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score. Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of 10.5\% in wall time. This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.
